### 2020-04-30 manuscript/manuscript.rmd
format supplementary text

```{r table_study_summary}
tableXXdistribution = read_tsv("../data_processed/tables/study_summary.tsv")
	kable(tableXXdistribution, caption= "Table 1. Overview of data matrices used in this study")

@@

```{r table_phylogenetic_signal}
tableXXdistribution = read_tsv("../trees_new/AU_test/summary.tsv")
	kable(tableXXdistribution, caption= "Supplementary Table 4. Distribution of phylogenetic signal for different models and outgroup choice")

**Extended Data Table 1.** The models selected by ModelFinder for each matrix.
```{r table_modelfinder}
analyses_new %>%
	filter(modelfinder==TRUE) %>%
	select( matrix, clade, result, model_summary ) %>%
	kable()

@@

## Supplementary Results

### Models of molecular evolution
Models of molecular evolution are assembled by selecting different options for all these different components. The models that are applied in practice are heavily influenced by computational costs, as well as convention. For example, on the questions considered here, CAT site-heterogeneous models of equilibrium frequency have only been used in combination with Poisson and GTR exchangeability matrices. LG and WAG exchangeability matrices have only been used with site homogeneous estimates of equilibrium frequency. This is further confused by the abbreviations that are used for models. Papers often discuss CAT and WAG models as if they are exclusive, but these particular terms apply to non-exclusive model components-- CAT refers to equilibrium frequency variation across sites and WAG a particular exchangeability matrix. In this literature, CAT is generally shorthand for Poisson+CAT and WAG is shorthand for WAG+homogeneous equilibrium frequency estimation. One could, though, run a WAG+CAT model, although the computation time is much longer than Poisson+CAT model. To avoid confusion on this point, we always specify the exchangeability matrix first, followed by modifiers that describe the accommodation of heterogeneity in equilibrium frequencies (*e.g.*, CAT).  Moreover, the Gamma-rate heterogeinity (G4) is used in almost every analysis conducted here. If there are no modifiers, then it is implied that site homogeneous models are used.

@@

### Details of published analyses

@@

### Data-recoding methods

>>>>

**Extended Data Table 1.** TTable 1. Overview of data matrices used in this study.
```{r table_study_summary}
tableXXdistribution = read_tsv("../data_processed/tables/study_summary.tsv")
	kable(tableXXdistribution)

@@

**Extended Data Table 2.** The models selected by ModelFinder for each matrix.
```{r table_modelfinder}
analyses_new %>%
	filter(modelfinder==TRUE) %>%
	select( matrix, clade, result, model_summary ) %>%
	kable()

@@

### S.1 Models of molecular evolution
Models of molecular evolution are assembled by selecting different options for all these different components. The models that are applied in practice are heavily influenced by computational costs, as well as convention. For example, on the questions considered here, CAT site-heterogeneous models of equilibrium frequency have only been used in combination with Poisson and GTR exchangeability matrices. LG and WAG exchangeability matrices have only been used with site homogeneous estimates of equilibrium frequency. This is further confused by the abbreviations that are used for models. Papers often discuss CAT and WAG models as if they are exclusive, but these particular terms apply to non-exclusive model components-- CAT refers to equilibrium frequency variation across sites and WAG a particular exchangeability matrix. In this literature, CAT is generally shorthand for Poisson+CAT and WAG is shorthand for WAG+homogeneous equilibrium frequency estimation. One could, though, run a WAG+CAT model, although the computation time is much longer than Poisson+CAT model. To avoid confusion on this point, we always specify the exchangeability matrix first, followed by modifiers that describe the accommodation of heterogeneity in equilibrium frequencies (*e.g.*, CAT).  Moreover, the Gamma-rate heterogeinity (G4) is used in almost every analysis conducted here. If there are no modifiers, then it is implied that site homogeneous models are used.

@@

### S.2 Details of published analyses

@@

### S.3 Data-recoding methods
